---
title: "HTKS EF Devsci analysis"
output:
 bookdown::html_document2:
    toc: yes
    number_sections: false
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=TRUE, warning=FALSE, message=FALSE)
```

```{r libraries, include=FALSE }
library(conflicted)

conflict_prefer("select", "dplyr")
conflict_prefer("filter", "dplyr")
conflict_prefer("as_factor", "sjlabelled")
conflict_prefer("corrplot", "corrplot")
conflict_prefer("standardize", "jtools")
conflict_prefer("cor_pmat", "rstatix")

libs = c('haven',
         'ggthemes','sjlabelled','patchwork', 'kableExtra','knitr','lme4','bookdown','generics','lubridate', 'nnet', 'foreign', 'sjPlot', 'ggeffects', 'sjmisc', 'VGAM', 'merTools', 'lmtest', 'glmmTMB', 'ggstance', 'gtsummary', 'ggforce', 'jtools', 'performance', 'see', 'arm', 'naniar','table1' ,'MuMIn', 'ggplot2', 'tidyverse', 'Hmisc', 'psych', 'RColorBrewer', 'ggpubr', 'rockchalk', 'corrplot', 'retrodesign', 'ggcorrplot', 'rstatix', 'olsrr') 

invisible(lapply(libs,library, character.only=T))

```

```{r importdata, include=FALSE }

DFsmall = readRDS('data/cleaneddata_shared-code.rds')

```


# Methods

## Table 1. Participant sample details, including age, BMI, years of schooling, and compulsory start age of school.

```{r tblsummary}

DFsmall %>%
  select(location, Sex = sex, Age = age_yr2, BMI = bmi, 'Years of Schooling' = edu_exposure) %>%
  gtsummary::tbl_summary(
    by = location, 
    statistic = c(Age, BMI, 'Years of Schooling') ~ "{mean} ({sd}) {min} - {max}",
    digits = c(Age, BMI, 'Years of Schooling') ~ 2,
    missing_text = "(Missing)"
  )

```

Compulsory years of schooling were added manually for each fieldsite in this table.

# Results

## *Summary Stats*

### Table 3.  Scores on the HTKS, Knox Cube, and Beads Tasks by site.

```{r descriptives tasks, echo = FALSE}
DFsmall %>%
  select(location, 'HTKS All' = HTKS_all, 'HTKS I & II' = HTKS_i_ii, 'Knox Cube' = knox_total, 'Beads' = beads_total) %>%
  gtsummary::tbl_summary(
    by = location, 
    type = list('HTKS All' ~ 'continuous2'),
    statistic = list(c('HTKS All') ~ c("{mean} ({sd})", "{median}"),
                     c('HTKS I & II', 'Knox Cube', 'Beads') ~ "{mean} ({sd})"), 
    digits = c('HTKS All','HTKS I & II', 'Knox Cube', 'Beads') ~ 2,
    missing_text = "(Missing)"
    ) %>% 
  add_overall()
  
```

### Figures 2a and 2b: Violin plots showing HTKS scores by study site. The dashed line represents the maximum possible score.

```{r ceiling plots, echo= FALSE}
#Create violin plot of HTKS scores (parts I, II, and III)
plot5 <- DFsmall %>%
  ggplot(aes(x=location, y=HTKS_all, fill=location)) +
    geom_violin() +
    geom_jitter(color="black", size=1, alpha=0.9) +
     theme_classic() +
    theme(
      plot.title = element_text(size=11)
    ) +
    ggtitle("HTKS (Parts I, II, & III) Scores by Site") +
    xlab("") + ylab("HTKS Total Score") +
   scale_fill_brewer(palette="RdBu") + 
  geom_hline(yintercept=60, linetype = "dashed") +
     labs(fill="Location")  +
  ylim(-.05, 60.05)

# Create violin plot of HTKS scores (parts I & II)
plot5_1 <- DFsmall %>%
  ggplot(aes(x=location, y=HTKS_i_ii, fill=location)) +
    geom_violin() +
    geom_jitter(color="black", size=1, alpha=0.9) +
     theme_classic() +
    theme(
      plot.title = element_text(size=11)
    ) +
    ggtitle("HTKS (Parts I & II) Scores by Site") +
    xlab("") + ylab("HTKS Total Score") +
   scale_fill_brewer(palette="RdBu") + 
  geom_hline(yintercept=40, linetype = "dashed") +
     labs(fill="Location") +
  ylim(-.05, 60.05) # Keep same y limits as first plot for comparison

# Combine plots side by side
plot_5_5_1 <- ggarrange(plot5, plot5_1, common.legend = TRUE, legend = "none", labels = c("A", "B"))

plot_5_5_1
```

Lets look at a scatter plot matrix for our most important variables

### Table 4. Results of five one-way ANOVAs for site-level differences in variables.

```{r ANOVAs}

anova_bmi <- aov(bmi ~ location, data = DFsmall)
summary(anova_bmi)
anova_age <- aov(age_yr ~ location, data = DFsmall)
summary(anova_age)
anova_edu <- aov(edu_exposure ~ location, data = DFsmall)
summary(anova_edu)
anova_knox <- aov(knox_total_z ~ location, data = DFsmall)
summary(anova_knox)
anova_beads <- aov(beads_total_z ~ location, data = DFsmall)
summary(anova_beads)

#Combining outputs together in a table
anova_sum <- rbind(
anova_summary(anova_bmi),
anova_summary(anova_age),
anova_summary(anova_edu),
anova_summary(anova_knox),
anova_summary(anova_beads)) %>% select(-c('p<.05','ges')) %>% as.data.frame()

# Replace effect column with correct effect names
anova_sum$IV <- as.character(c('BMI (m/kg^2)','Age (years)','Years of Schooling (years)', 'Knox Cube Score (z-scored)','Beads Score (z-scored)')) # Create column naming independent variable
anova_sum <- anova_sum %>% 
  select(IV,DFn, DFd, F, p) %>% 
  kable(.) %>%
  kable_styling(bootstrap_options = c("striped", "hover")) 

# Print table
anova_sum
```

### Table 5. Summary of Tukey’s HSD posthoc tests for demographic and cognitive variables and location.

Because all of our demographic/cognitive variables are significantly different by site (see Table 4 anovas), we're running posthoc tests (Tukey's HSD) to review specific site-site differences.

Posthoc results were combined into a single table by hand to maximize efficient use of space. Here, we will show full results of each posthoc test, including confidence intervals, for each ANOVA.

Tukey's HSD - BMI:
```{r Tukey}
TukeyHSD(anova_bmi)
```

Tukey's HSD - Age:
```{r}
TukeyHSD(anova_age)
```

Tukey's HSD - Years of Schooling:
```{r}
TukeyHSD(anova_edu)
```

Tukey's HSD - Knox Score:
```{r}
TukeyHSD(anova_knox)
```

Tukey's HSD - Beads Scores:
```{r}
TukeyHSD(anova_beads)
```


### Figures 3a-d. Site-level distributions of years of schooling and task scores (HTKS, Knox Cube, and Beads).
```{r score plots by location, echo= FALSE}
# Generate HTKS scores by site plot
plot_01 <- DFsmall %>%
 ggplot(aes(x=location, y=HTKS_all, fill=location)) +
    geom_boxplot() +
    #geom_jitter(color="black", size=1, alpha=0.9) +
     theme_classic() +
    theme(
     plot.title = element_text(size=11),
     axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank()
    ) +
    ggtitle("HTKS Scores by Site") +
    xlab("") + ylab("HTKS Total Score") +
   scale_fill_brewer(palette="RdBu") +
     labs(fill="Location")

# Generate years of schooling by site plot
plot_01_01 <- DFsmall %>%
 ggplot(aes(x=location, y=yrs_school, fill=location)) +
    geom_boxplot() +
    #geom_jitter(color="black", size=1, alpha=0.9) +
     theme_classic() +
    theme(
     plot.title = element_text(size=11),
     axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank()
    ) +
    ggtitle("Years of Schooling by Site") +
    xlab("") + ylab("Years of Schooling") +
   scale_fill_brewer(palette="RdBu") +
     labs(fill="Location")

# Generate beads scores by site plot
plot_02 <- DFsmall %>%
 ggplot(aes(x=location, y=beads_total, fill=location)) +
    geom_boxplot() +
    #geom_jitter(color="black", size=1, alpha=0.9) +
     theme_classic() +
    theme(
     plot.title = element_text(size=11),
     axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank()
    ) +
    ggtitle("Beads Score by Site") +
    xlab("") + ylab("Beads Score") +
   scale_fill_brewer(palette="RdBu") +
     labs(fill="Location")

# Generate knox scores by site plot
plot_03 <- DFsmall %>%
 ggplot(aes(x=location, y=knox_total, fill=location)) +
    geom_boxplot() +
    #geom_jitter(color="black", size=1, alpha=0.9) +
  theme_classic() +
    theme(
     plot.title = element_text(size=11),
     axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank()) +
    ggtitle("Knox Cube Score by Site") +
    ylab("Knox Cube Score") +
   scale_fill_brewer(palette="RdBu") +
     labs(fill="Location")

# Combine 4 plots
combined_plot = ggarrange(plot_01_01, #yrs of school on first row
          ggarrange(plot_01, plot_02, plot_03, ncol = 3, labels = c("B", "C", "D"), legend = "none"), # HTKS, beads, and knox plots on second row
          nrow = 2, 
          labels = "A"   
          ) 

# Print plot
combined_plot
```

## *Is there a relationship between HTKS performance and EFs (as measured by the Knox Cube and Beads Tasks) across all sites?*

### Figure 4. Pearson Correlations for HTKS, Knox Cube Task, and Beads Task scores.


Here we create the correlation matrix:


```{r correlation mat, fig.height=5, fig.width=5}
#Select only continuous variables for correlation analysis
dfcorrs = DFsmall %>% select(HTKS_all,HTKS_i_ii, knox_total, beads_total, edu_exposure, age_yr, bmi) %>% drop_na()

colnames(dfcorrs) <- c('HTKS all','HTKS I & II', 'Knox Cube Total', 'Beads Total', 'Years of Schooling','Age', 'BMI') #Names of columns to be used in plots


dfcorrs.rcorr = rcorr(as.matrix(dfcorrs)) #Create correlation matrix

dfcorrs.coeff = dfcorrs.rcorr$r #Save corr coefficients
dfcorrs.p = dfcorrs.rcorr$P #Save corr p-values


grey <- adjustcolor("#696969", alpha.f = 0.6) #Create grey with adjusted opacity

#Make correlation plot
corrplot(dfcorrs.coeff, 
         method = "circle", 
         type = "lower", 
         title = "Correlation Matrix of Continuous Variables", mar=c(0,0,2,0), 
         p.mat = dfcorrs.p, addCoef.col = "black", #Add significance values
         insig = "pch", pch = 4, pch.col = grey, pch.cex = 2, #Add x's to insignificant correlations
         tl.col = "black", tl.pos = "ld") #Position/color for text labels
```

### Figure 5a & b. Scatterplots of Knox Cube and Beads scores against HTKS scores, respectively.

```{r scatterplots varying slopes knox}
#Create plot 5a
plot3 = ggplot(DFsmall, aes(knox_total, HTKS_all, color=location)) +
  stat_smooth(method="glm", family = binomial, formula=y~x,
              alpha=0.2, size=2, aes(fill=location)) +
  geom_point(position=position_jitter(height=0.02, width=0.02),size=3, alpha=0.3) +
  coord_cartesian(ylim = c(19.95, 60.05), , xlim = c(-.05, 15.05))+
  theme_minimal()+  
  ylab("HTKS Total (out of 60)") +
  xlab("Knox Cube Total (out of 15)") +
  theme(axis.title = element_text(angle = 90, vjust = -0.075),
        axis.title.x = element_text(angle = 0, size = 20),
        axis.title.y = element_text(size = 20),
        axis.text = element_text(size = 16),
        legend.text = element_text(size = 16),
        legend.title = element_text(size = 16),
        plot.title = element_text(size = 20, face = "bold"))+
  theme(strip.text.x = element_text(size = 18, colour = "black", angle = 0),
        strip.text.y = element_text(size = 18, colour = "black", angle = 270)) +
  scale_color_brewer(palette="RdBu")
```

```{r scatterplots varying slopes beads}
#Create plot 5b
plot4 = ggplot(DFsmall, aes(beads_total, HTKS_all, color=location)) +
  stat_smooth(method="glm", family = binomial, formula=y~x,
              alpha=0.2, size=2, aes(fill=location)) +
  geom_point(position=position_jitter(height=0.02, width=0.02),size=3, alpha=0.3) +
  coord_cartesian(ylim = c(19.95, 60.05), , xlim = c(-.05, 10.05))+
  theme_minimal()+  
  ylab("HTKS Total (out of 60)") +
  xlab("Beads Total (out of 10)") +
  theme(axis.title = element_text(angle = 90, vjust = -0.075),
        axis.title.x = element_text(angle = 0, size = 20),
        axis.title.y = element_text(size = 20),
        axis.text = element_text(size = 16),
        legend.text = element_text(size = 16),
        legend.title = element_text(size = 16),
        plot.title = element_text(size = 20, face = "bold"))+
  theme(strip.text.x = element_text(size = 18, colour = "black", angle = 0),
        strip.text.y = element_text(size = 18, colour = "black", angle = 270)) +
  scale_color_brewer(palette="RdBu")
```

```{r combined_beads knox and htks, fig.height = 5, fig.width = 10}
# Combine plots 5a & b
plot_3_4 <- ggarrange(plot3, plot4, common.legend = TRUE, legend = "right", labels = c("A", "B"))
plot_3_4
```


### Table 6. Results of the full model of independent variables and HTKS scores

*Is there a relationship between HTKS performance and EFs (as measured by the Knox and Beads tasks) in our overall sample?*

We'll first run the full model to answer this question. Here, we're running the model itself first.

```{r full model}
#Run full model
mboth = lm(HTKS_all ~ age_yr_c + sex + bmi_c + yrs_school_c + location + beads_total_z + knox_total_z,  data=DFsmall, na.action = na.fail) 
```

#### Check assumptions

Now, we'll check the assumption - resid plots, VIFs, and formal test for heteroskedasticity with the studentized Breusch-Pagan test.

```{r full model checks}
#Residual and Q-Q plot
par(mfrow=c(2,2)) # init 4 charts in 1 panel
plot(mboth)

#Check variance inflation factors for parameters
car::vif(mboth)

#BP test
bptest(mboth)
```

Looks like VIFs all look good, ranging from 1-1.6, so no concerns there.

The residual plot does look to be heteroskedastic, which is confirmed by a BP test. To account for this, we will calculate robust standard errors and confidence intervals.

```{r full model summary}
#Model parameters, where SE, CI and p-values are based on robust estimation
tab_model(mboth, vcov.fun = "HC", show.se = TRUE)

#Calculate AICc score
MuMIn::AICc(mboth)
```

### Table 7. Best fit model of independent variables and HTKS scores

This section is running a model selection process from all possible parameter combinations. This did not include interaction terms - interactions of interest are examined later.

```{r model selection with mumin}
# run model selection by AICc
model_sel <- dredge(mboth) #dredge from full model

# Show top 10 models
model_sel[1:10]

# Pull best fitting model
best_model <- get.models(model_sel, subset = 1)[[1]]
```

#### Check assumptions

Like above, we'll check resid plots, VIFs, and test for heteroskedasticity with the studentized Breusch-Pagan test.

```{r best model checks}
#Residual and Q-Q plot
par(mfrow=c(2,2)) # init 4 charts in 1 panel
plot(best_model)

#Check variance inflation factors for parameters
car::vif(best_model)

#BP test
bptest(best_model)
```

Looks like heteroskedasticity is also a problem here, so we will calculate robust standard errors.

```{r best model summary}
#Model summary table
tab_model(best_model, vcov.fun = "HC", show.se = TRUE)

#Calculate aicc
MuMIn::AICc(mboth)
```

## *Does formal education impact the relationship between HTKS and EF tasks?*

### Figure 6. Comparison of full model and years of schooling moderation effect models.

Running a moderation analysis to assess years of schooling as a moderator of location effects, Knox Cube, or Beads effect

```{r}

#Interactions - yrs school and location
mboth_int_loc = lm(HTKS_all ~ age_yr_c + sex + bmi_c + yrs_school_c + location + yrs_school_c*location + beads_total_z + knox_total_z,  data=DFsmall)
car::vif(mboth_int_loc)
tab_model(mboth_int_loc)

#Interactions - yrs school and knox
mboth_int_knox = lm(HTKS_all ~ age_yr_c + sex + bmi_c + yrs_school_c + location + beads_total_z + knox_total_z + yrs_school_c*knox_total_z,  data=DFsmall)
car::vif(mboth_int_knox)
tab_model(mboth_int_knox)

#Interactions - yrs school and beads
mboth_int_beads = lm(HTKS_all ~ age_yr_c + sex + bmi_c + yrs_school_c + location + beads_total_z + knox_total_z + yrs_school_c*beads_total_z,  data=DFsmall)
car::vif(mboth_int_beads)
tab_model(mboth_int_beads)

#Check AICc values for all 3 interaction models
MuMIn::AICc(mboth_int_loc, mboth_int_knox, mboth_int_beads)
```

Below display the interaction models against the full model to check for differences in effects. Effects are unmoderated by years of schooling (see how little effects change across all models).

```{r coefplot, fig.cap='Plots of coefficients for each of the four models compared in this analysis. Each model is a linear regression with normal errors.', fig.height=7, fig.width=9}
# To visually display the coefficients from main and interaction models at once 

coef.names <- c("Age"="age_yr_c", "Sex:M"="sexm","BMI"="bmi","Years of Schooling"="yrs_school_c",
                 "Loc:Ghana"="locationGhana","Loc:Vanuatu"="locationVanuatu", 
                "Loc:Malaysia"="locationMalaysia", "Beads Score"="beads_total_z",
                "Knox Cube Score"="knox_total_z","Years of School*Loc:Ghana"="yrs_school_c:locationGhana",
              "Years of School*Loc:Vanuatu"= "yrs_school_c:locationVanuatu",
              "Years of School*Loc:Malaysia"= "yrs_school_c:locationMalaysia", 
               "Years of School*Knox Cube"= "yrs_school_c:knox_total_z",
              "Years of School*Beads"= "yrs_school_c:beads_total_z")
                
mod_regression_plot <- plot_summs(mboth, mboth_int_loc, mboth_int_knox, mboth_int_beads, 
                                  exp = FALSE, 
                                  model.names = c('Full Model', 'Add Years of School*Location',
                                                  'Add Years of School*Knox', 
                                                  'Add Years of School*Beads,'), 
                                  coefs = coef.names, 
                                  point.shape = FALSE,
                                  robust = TRUE)  + 
  theme_minimal() + 
  labs(x = "Coefficient", y = 'Variable', title = 'Comparison of Moderation Models') + 
  scale_shape_manual(values=c(20,20,20,20), guide = FALSE) +
  scale_color_brewer(palette="RdBu")

mod_regression_plot
```

## *Effect of experimental variation in task environment and administration?*

### Table 8. Linear model results examining the number of practice trials and HTKS performance

```{r exp variation trials, echo=FALSE}
#Total practice trials
DFsmall = DFsmall %>%
 mutate(
    HTKS_practice = as_numeric(part_i_pr+part_ii_pr+part_iii_pr))

# Model practice trials predicting HTKS
practice_model <- lm(HTKS_all ~ HTKS_practice, DFsmall)
tab_model(practice_model)

```

Looks like the practice trials aren't an influence on HTKS scores from this model, so we won't worry about them.

### Figures 7a & 7b. Background noise level and EF task scores across sites

Background noise was rated as 0,1,2 by coders. 0 = silent/lab-like setting 1 = intermittent noise or constant low level noise 2 = loud background noise (yelling, lots of talking, etc.)

To look at whether the EF task totals are different based on background noise levels, we'll look at the data and run an ANOVA for the Knox task total score and the Beads Task total score.

```{r exp variation noise, echo=FALSE}
#Background noise and EF scores

# Compute the analysis of variance for knox
res.aov_knox <- aov(knox_total ~ back_noise_knox, data = DFsmall)
# Summary of the analysis
summary(res.aov_knox)

# Compute the analysis of variance for bead
res.aov_beads <- aov(beads_total ~ back_noise_beads, data = DFsmall)
# Summary of the analysis
summary(res.aov_beads)

```

Now we'll plot these:

```{r exp variation noise boxplots, fig.height = 6, fig.width = 11, echo=FALSE}
#Knox boxplots
noise_knox <- DFsmall %>% filter(!is.na(back_noise_knox))
noise_knox_boxplot <- ggplot(noise_knox, aes(x=back_noise_knox, y=knox_total, fill = back_noise_knox)) + 
  geom_boxplot(show.legend = FALSE) +
    #outlier.colour="black", outlier.shape=16, outlier.size=2, 
    #notch=FALSE) + 
  scale_fill_brewer(palette="RdBu") +
  theme_classic() + ggtitle("Background Noise & Knox Cube Scores") +
  ylab("Knox Cube Task Score (out of 15)") +
  xlab("Background Noise Level")

#Beads boxplots
noise_beads <- DFsmall %>% filter(!is.na(back_noise_beads))
noise_beads_boxplot <- ggplot(noise_beads, aes(x=back_noise_beads, y=beads_total, fill = back_noise_beads)) + 
  geom_boxplot(show.legend = FALSE) +
    scale_fill_brewer(palette="RdBu") +
  theme_classic() + ggtitle("Background Noise & Beads Task Scores") +
  ylab("Beads Task Score (out of 10)") +
  xlab("Background Noise Level")

#combine both for final figs
plot_noise_comb <- ggarrange(noise_knox_boxplot, noise_beads_boxplot, labels = c("A", "B"))
plot_noise_comb
```

Looks like there isn't significant differences between the groups here, which makes sense based on the visuals. Note there are quite a few missing values, particularly for the Knox Test (43).

# Suppplemental Materials

### Table Supp2. Comparisons of Linear Models

### Figure Supp1. Residual graphs of Model 3 (HTKS score predicted by age, sex, BMI, years of schooling, Knox Cube Score, and Beads Score)

```{r Supp1 full model qq plot}
#Residual and Q-Q plot
par(mfrow=c(2,2)) # init 4 charts in 1 panel
plot(mboth)
```

### Table Supp3. Results of Model 1, including age, sex, BMI, and location variables

Here and for each model below this we will output the main model table, GVIFs, and AICc

```{r Supp3 Model 1 base table}

# save model
mbase <- lm(HTKS_all ~ age_yr_c + sex + bmi_c + location,  data=DFsmall)

# output table w/ robust SE
tab_model(mbase, vcov.fun = "HC", show.se = TRUE)

# VIF/GVIFs
car::vif(mbase)

#Calculate aicc
MuMIn::AICc(mbase)
```

### Table Supp4. Results of Model 2, including age, sex, BMI, years of schooling, and location variables

```{r Supp4 Model 2 table}

# save model
mbase_sch <- mbase_sch <- lm(HTKS_all ~ age_yr_c + sex + bmi_c + yrs_school_c + location,  data=DFsmall)

# output table w/ robust SE
tab_model(mbase_sch, vcov.fun = "HC", show.se = TRUE)

# VIF/GVIFs
car::vif(mbase_sch)

#Calculate aicc
MuMIn::AICc(mbase_sch)
```

### Table Supp5. Results of Model 3, including age, sex, BMI, location, Knox Cube score, and Beads score variables.


```{r Supp5 Model 3 table}

# save model
mbothns  = lm(HTKS_all ~ age_yr_c + sex + bmi_c + location + beads_total_z + knox_total_z,  data=DFsmall)

# output table w/ robust SE
tab_model(mbothns, vcov.fun = "HC", show.se = TRUE)

# VIF/GVIFs
car::vif(mbothns)

#Calculate aicc
MuMIn::AICc(mbothns)
```

### Table Supp6. Results of Model 5, including age, sex, BMI,years of schooling,location, and Knox Cube score variables

```{r Supp6 Model 5 table}

# save model
mknox = lm(HTKS_all ~ age_yr_c + sex + bmi_c + yrs_school_c + location + knox_total_z,  data=DFsmall)

# output table w/ robust SE
tab_model(mknox, vcov.fun = "HC", show.se = TRUE)

# VIF/GVIFs
car::vif(mknox)

#Calculate aicc
MuMIn::AICc(mknox)
```

### Table Supp7. Results of Model 6, including age, sex, BMI, years of schooling, location, and Beads score variables.

```{r Supp7 Model 6 table}

# save model
mbeads = lm(HTKS_all ~ age_yr_c + sex + bmi_c + yrs_school_c + location + beads_total_z,  data=DFsmall)

# output table w/ robust SE
tab_model(mbeads, vcov.fun = "HC", show.se = TRUE)

# VIF/GVIFs
car::vif(mbeads)

#Calculate aicc
MuMIn::AICc(mbeads)
```
### Table Supp8. Results of exploratory model selection process

```{r model selection table}

# Display top 10 models from 'dredge' w lowest AICc
model_sel[1:10]
```

